Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2017-01-21 WRITEUP/ms_arxiv/ms.tex
arvix version (lossy figures), work with ArXIV

\documentclass[]{emulateapj}
\usepackage{amsmath}

\usepackage[normalem]{ulem}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}}

\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{etoolbox}

@@

\makeatother
%
\usepackage{xspace}
%
\usepackage{apjfonts}
\usepackage{amssymb, amsmath} % for e.g. \lesssim
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros} % for understanding Journal in bib
\usepackage{graphics,graphicx}
%
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\mbh}{\mbox{$M_{\rm BH}$}\xspace}
\newcommand{\mdyn}{\mbox{$M_{\rm dyn}$}\xspace}
\newcommand{\mbulge}{\mbox{$M_{\rm bulge}$}\xspace}
\newcommand{\mstar}{\mbox{$M^*$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\Rsun}{\mbox{$R_{\odot}$}\xspace}
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
%
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\aco}{\mbox{CO($J$\,=\,1\,\rarr\,0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$\,=\,2\,\rarr\,1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$\,=\,3\,\rarr\,2)}\xspace}
\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}}
%
\newcommand{\cii}{[C{\scriptsize II}]}
\newcommand{\mgii}{\mbox{Mg{\scriptsize II}~2798\AA}\xspace}
\newcommand{\oiii}{\mbox{$[$O{\scriptsize III}$]$~4959, 5007\AA}\xspace}
\newcommand{\oii}{\mbox{$[$O{\scriptsize II}$]$~3727\AA}\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}\xspace}
\newcommand{\kms}{\mbox{km\,s$^{-1}$}\xspace}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\alphaco}{\mbox{$\alpha_{\rm CO}$}\xspace}
\newcommand{\alphaU}{\mbox{$M_{\odot}~($K\,\,km\,\,pc$^2)^{-1}$}\xspace}
\newcommand{\sfrU}{\mbox{\Msun\,yr$^{-1}$}\xspace}
% Numerical values
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\petm}[2]{$^{+#1}_{-#2}$}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
%
\newcommand{\eg}{{e.g.,~}}
\newcommand{\ie}{{i.e.,~}}
%
\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\Sec}[1]{\S\ref{sec:#1}}
%
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}
\newcommand\tnl{\,\tablenotemark{l}}
%
\def\herschel {{\it Herschel Space Observatory}\xspace}
\def\hst {{\it Hubble Space Telescope}\xspace}
\def\alma     {Atacama Large (sub-)Millimeter Array (ALMA)\xspace}
\def\spitzer {{\it Spitzer Space Telescope}\xspace}
\def\pdbi     {Plateau de Bure Interferometer\xspace}
\def\carma    {Combined Array for Research in Millimeter-wave Astronomy\xspace}
\def\cso      {Caltech Sumillimeter Observatory (CSO)\xspace}
\def\noema    {Northern Extended Millimeter Array (NOEMA)\xspace}
\def\vla      {{\it Karl G. Jansky} Very Large Array\xspace}
% Typography
\newcommand{\ncode}[1]{{\sc #1}}
% Codes / Softwares
\newcommand{\uvmcmcfit}{\ncode{uvmcmcfit}\xspace}
\def\aips {\ncode{AIPS}\xspace}
\def\casa {\ncode{CASA}\xspace}
% Long words
\newcommand{\obs}{observations\xspace}
\newcommand{\lowZ}{low-metallicity\xspace}
\newcommand{\mulw}{multi-wavelength\xspace}
\newcommand{\SF}{star formation\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\SBs}{starbursts\xspace}
\newcommand{\gl}{gravitationally lensed\xspace}
\newcommand{\MCMC}{Markov Chain Monte Carlo (MCMC)\xspace}
\newcommand{\ms}{``main-sequence''\xspace}
% Wavelength regimes
\newcommand{\fir}{far-IR\xspace}
\newcommand{\fuv}{far-UV\xspace}
\newcommand{\mir}{mid-IR\xspace}
\newcommand{\nir}{near-IR\xspace}

@@

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{f1.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment in steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{f3.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is the same as in \Fig{CO21spec}.
The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.eps}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment in steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to $\pm2^n\sigma$, where
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer running from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{f5.eps}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
light blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axes are shown on a log scale.
\label{fig:delensed}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\begin{tabular}{c}
\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{f6a.eps} \\
\includegraphics[width=0.98\textwidth]{f6b.eps}
\end{tabular}
\caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
Top: each panel corresponds to a channel map of width 107.5\,\kms centered on the indicated velocity.
The observed emission (red contours) is over-plotted atop the best-fit model (grayscale).
Bottom: residual images obtained by
taking a Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain.
In all panels, the location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line; locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses; the caustic curves are represented as cyan lines.
Contours start
at $\pm$3$\sigma$ and increment in steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
The beam of the PdBI observations is shown in the bottom right corner.
The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
The best-fit model of the red-most channel (top left panel) contains two source components --- RXJ1131 and its companion galaxy.
\label{fig:model}}
\end{figure*}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{f7.eps}
\caption{
Channel maps of the PdBI \bco data at 22\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment in steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{f8.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5).
The spectra map covers an extent of $\sim$10''$\times$10''
centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
Spatial offset in arcsec is denoted in top left corner of each panel.
The velocity and flux density scales are denoted in the top right panel.
\label{fig:spatialSpec}}
\end{figure*}

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
346\,$-$\,260       & 6.7 $\pm$ 2.5 &  7.2 $\pm$ 5.6 \\
238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
\end{deluxetable}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{f9a.pdf}
\includegraphics[width=0.525\textwidth]{f9b.eps}
\caption{Velocity gradient of the \bco emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
Left: source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown
as markers
atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}).
The markers are color-coded by their centroid velocities.
The contours are in steps of 50\,\kms.
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on
the reconstructed source-plane velocity gradient.
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions along the major axis.
\label{fig:PV}}
\end{figure*}

>>>>

\documentclass[]{emulateapj}
 \usepackage[colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{etoolbox}

@@

 \makeatother
%
\usepackage{xspace}
%
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
%\usepackage{graphics,graphicx}
%
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\mbh}{\mbox{$M_{\rm BH}$}\xspace}
\newcommand{\mdyn}{\mbox{$M_{\rm dyn}$}\xspace}
\newcommand{\mbulge}{\mbox{$M_{\rm bulge}$}\xspace}
\newcommand{\mstar}{\mbox{$M^*$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\Rsun}{\mbox{$R_{\odot}$}\xspace}
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
%
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\aco}{\mbox{CO($J$\,=\,1\,\rarr\,0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$\,=\,2\,\rarr\,1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$\,=\,3\,\rarr\,2)}\xspace}
\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}}
%
\newcommand{\cii}{[C{\scriptsize II}]}
\newcommand{\mgii}{\mbox{Mg{\scriptsize II}~2798\AA}\xspace}
\newcommand{\oiii}{\mbox{$[$O{\scriptsize III}$]$~4959, 5007\AA}\xspace}
\newcommand{\oii}{\mbox{$[$O{\scriptsize II}$]$~3727\AA}\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}\xspace}
\newcommand{\kms}{\mbox{km\,s$^{-1}$}\xspace}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\alphaco}{\mbox{$\alpha_{\rm CO}$}\xspace}
\newcommand{\alphaU}{\mbox{$M_{\odot}~($K\,\,km\,\,pc$^2)^{-1}$}\xspace}
\newcommand{\sfrU}{\mbox{\Msun\,yr$^{-1}$}\xspace}
% Numerical values
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\petm}[2]{$^{+#1}_{-#2}$}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
%
\newcommand{\eg}{{e.g.,~}}
\newcommand{\ie}{{i.e.,~}}
%
\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\Sec}[1]{\S\ref{sec:#1}}
%
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}
\newcommand\tnl{\,\tablenotemark{l}}
%
\def\herschel {{\it Herschel Space Observatory}\xspace}
\def\hst {{\it Hubble Space Telescope}\xspace}
\def\alma     {Atacama Large (sub-)Millimeter Array (ALMA)\xspace}
\def\spitzer {{\it Spitzer Space Telescope}\xspace}
\def\pdbi     {Plateau de Bure Interferometer\xspace}
\def\carma    {Combined Array for Research in Millimeter-wave Astronomy\xspace}
\def\cso      {Caltech Sumillimeter Observatory (CSO)\xspace}
\def\noema    {Northern Extended Millimeter Array (NOEMA)\xspace}
\def\vla      {{\it Karl G. Jansky} Very Large Array\xspace}
% Typography
\newcommand{\ncode}[1]{{\sc #1}}
% Codes / Softwares
\newcommand{\uvmcmcfit}{\ncode{uvmcmcfit}\xspace}
\def\aips {\ncode{AIPS}\xspace}
\def\casa {\ncode{CASA}\xspace}
% Long words
\newcommand{\obs}{observations\xspace}
\newcommand{\lowZ}{low-metallicity\xspace}
\newcommand{\mulw}{multi-wavelength\xspace}
\newcommand{\SF}{star formation\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\SBs}{starbursts\xspace}
\newcommand{\gl}{gravitationally lensed\xspace}
\newcommand{\MCMC}{Markov Chain Monte Carlo (MCMC)\xspace}
\newcommand{\ms}{``main-sequence''\xspace}
% Wavelength regimes
\newcommand{\fir}{far-IR\xspace}
\newcommand{\fuv}{far-UV\xspace}
\newcommand{\mir}{mid-IR\xspace}
\newcommand{\nir}{near-IR\xspace}

@@

\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{f1.pdf}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.pdf}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.pdf}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.pdf}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment in steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{f3.pdf}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is the same as in \Fig{CO21spec}.
The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.pdf}
\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.pdf}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment in steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to $\pm2^n\sigma$, where
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer running from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{f5.pdf}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
light blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axes are shown on a log scale.
\label{fig:delensed}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\begin{tabular}{c}
\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{f6a.pdf} \\
\includegraphics[width=0.98\textwidth]{f6b.pdf}
\end{tabular}
\caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
Top: each panel corresponds to a channel map of width 107.5\,\kms centered on the indicated velocity.
The observed emission (red contours) is over-plotted atop the best-fit model (grayscale).
Bottom: residual images obtained by
taking a Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain.
In all panels, the location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line; locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses; the caustic curves are represented as cyan lines.
Contours start
at $\pm$3$\sigma$ and increment in steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
The beam of the PdBI observations is shown in the bottom right corner.
The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
The best-fit model of the red-most channel (top left panel) contains two source components --- RXJ1131 and its companion galaxy.
\label{fig:model}}
\end{figure*}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{f7.pdf}
\caption{
Channel maps of the PdBI \bco data at 22\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment in steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{f8.pdf}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5).
The spectra map covers an extent of $\sim$10''$\times$10''
centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
Spatial offset in arcsec is denoted in top left corner of each panel.
The velocity and flux density scales are denoted in the top right panel.
\label{fig:spatialSpec}}
\end{figure*}

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Velocity Range (\kms)} &
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
346\,$-$\,260       & 6.7 $\pm$ 2.5 &  7.2 $\pm$ 5.6 \\
238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
\end{deluxetable}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{f9a.pdf}
\includegraphics[width=0.525\textwidth]{f9b.pdf}
\caption{Velocity gradient of the \bco emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
Left: source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown
as markers
atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}).
The markers are color-coded by their centroid velocities.
The contours are in steps of 50\,\kms.
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on
the reconstructed source-plane velocity gradient.
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions along the major axis.
\label{fig:PV}}
\end{figure*}
